Analysis Pipeline

### 2025-06-24 analysis_pipeline.Rmd
Korrigiere fehlende Scatter-Daten im Pipeline-Notebook

```{r}
mods <- fit_models(prep$S, config)
```

@@

```{r}
scat <- make_scatter_data(mods, prep$S)
scat_plots <- plot_scatter(scat)
```

>>>>

```{r}
mods <- fit_models(prep$S, config)
mods_p <- fit_models(prep$S_perm, config)
```

@@

```{r}
scat_n <- make_scatter_data(mods, prep$S)
scat_p <- make_scatter_data(mods_p, prep$S_perm)
scat <- c(scat_n, setNames(scat_p, paste0(names(scat_p), "_p")))
scat_plots <- plot_scatter(scat)
```
